Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-04-25 products/manuscript/Manuscript.qmd
Tab1
IMGs

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# 1) Load here() before you call i_am()
library(here)

# 2) Tell here() where this document lives, relative to the project root.
#    (Your project root is "Joseph-MADA-project", so we point to "products/manuscript/Manuscript.qmd")
here::i_am("products/manuscript/Manuscript.qmd")

# 3) (Optional) now load knitr and set the knit root to the project root
library(knitr)
opts_knit$set(root.dir = here::here())

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics(here::here("Images", "Table 1. Baseline Characteristics .png"))

@@

```{r,echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics(here::here("Images", "Table4.Interaction Malaria vsIPTP.png"))

>>>>

```{r setup, include=FALSE}
# 1) identify project root for here()
library(here)
here::i_am("products/manuscript/Manuscript.qmd")

# 2) tell knitr to use that root (so all relative paths start there)
library(knitr)
knitr::opts_knit$set(root.dir = here::here())
```

@@

```{r fig-table1, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table1Baseline.png")

@@

```{r,echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table4Interaction.png")
```
